---
title: "Técnicas de  clustering aplicado al estudio de variantes de genomas virales"
output:
  html_document: default
  html_notebook:
    code_folding: hide
    fig_height: 6
    fig_width: 10
---



```{r  message=FALSE, warning=FALSE, setup}
#librerias necesarias


#library (Biostrings) # Manipulacion de secuencias y alineamientos

library(ggplot2)
library(plotly)
library (RColorBrewer)

library(tidyr)
library(dplyr)
#library(reshape2)
library(psych)
library(irlba)
library(fpc)

```



### Data
```{r warning= FALSE, message=FALSE }
train<-read.csv("/home/sergio/Documents/KAGGLE/CervicalCancerScreening/output/features/Andrei/old/ccs.pipelines.example_pipeline.ChantaPipeline_train_.csv", stringsAsFactors = FALSE)%>%
          select(-X)%>%
              mutate(id=as.numeric(gsub(".jpg","",image_name)))
test<-read.csv("/home/sergio/Documents/KAGGLE/CervicalCancerScreening/output/features/Andrei/old/ccs.pipelines.example_pipeline.ChantaPipeline_test_.csv" , stringsAsFactors = FALSE)%>%
            select(-X)%>%
              mutate(id=as.numeric(gsub(".jpg","",image_name)))

```

### Explore  features names
```{r warning= FALSE, message=FALSE }
#length(grep("pixel",colnames(train), value=TRUE))
train_index<-train%>% dplyr::select(type_cat,image_name,id)
test_index<-test%>% dplyr::select(image_name,id)
#Remove type_cat
train<-train%>% dplyr::select(-type_cat,-image_name)
test<-test%>% dplyr::select(-image_name)

#Feature segementation for exploration and transformation
feat_pixel_train<- train%>% dplyr::select(starts_with("pixel"))
feat_pixel_test<- test%>% dplyr::select(starts_with("pixel"))
feat_X3D_train<- train%>% dplyr::select(starts_with("X3D"))
feat_X3D_test<- test%>% dplyr::select(starts_with("X3D"))
feat_rest_train<- train%>% dplyr::select(-starts_with("pixel"),-starts_with("X3D"))
feat_rest_test<- test%>% dplyr::select(-starts_with("pixel"),-starts_with("X3D")) 

```




### Filter invariant features
```{r warning= FALSE, message=FALSE }
#Check near Zero variance features
library(caret)
#NoVar<-nearZeroVar(feat_pixel,saveMetrics= TRUE)
#NoVar<-nearZeroVar(feat_X3D,saveMetrics= TRUE)

### REST
nzv_11 <- nearZeroVar(feat_rest_train)
nzv_12 <- nearZeroVar(feat_rest_test)
if(length(unique(c(nzv_11,nzv_12)))>0)
      {
        feat_rest_train<- feat_rest_train[, -unique(c(nzv_11,nzv_12))]
        feat_rest_test<- feat_rest_test[, -unique(c(nzv_11,nzv_12))]
        }

### PIXEL
nzv_21<- nearZeroVar(feat_pixel_train)
nzv_22 <- nearZeroVar(feat_pixel_test)

if(length(unique(c(nzv_21,nzv_22)))>0)
      {
        feat_pixel_train<- feat_pixel_train[, -unique(c(nzv_21,nzv_22))]
        feat_pixel_test<- feat_pixel_test[, -unique(c(nzv_21,nzv_22))]
        }


### X3D
nzv_31 <- nearZeroVar(feat_X3D_train)
nzv_32 <- nearZeroVar(feat_X3D_test)

if(length(unique(c(nzv_31,nzv_32)))>0)
      {
        feat_X3D_train<- feat_X3D_train[, -unique(c(nzv_31,nzv_32))]
        feat_X3D_test<- feat_X3D_test[, -unique(c(nzv_31,nzv_32))]
}


```


### Data
```{r warning= FALSE, message=FALSE }


##Check the mean and sd of every columnn in train and test
head(cbind(train.mean = lapply(feat_rest_train[,-1], mean),
          train.sd = lapply(feat_rest_train[,-1], sd),
                test.mean = lapply(feat_rest_test[,-1], mean),
                      test.sd = lapply(feat_rest_test[,-1], sd)))
##Check the mean and sd of every columnn in train and test
head(cbind(train.mean = lapply(feat_X3D_train[,-1], mean),
          train.sd = lapply(feat_X3D_train[,-1], sd),
                test.mean = lapply(feat_X3D_test[,-1], mean),
                      test.sd = lapply(feat_X3D_test[,-1], sd)))
##Check the mean and sd of every columnn in train and test
head(cbind(train.mean = lapply(feat_pixel_train[,-1], mean),
          train.sd = lapply(feat_pixel_train[,-1], sd),
                test.mean = lapply(feat_pixel_test[,-1], mean),
                      test.sd = lapply(feat_pixel_test[,-1], sd)))

```

### correlation  ~rest features
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }

#scale train
feat_rest_train_s<- scale(as.matrix(feat_rest_train%>%select(-creation_time))
                                                                  , center=TRUE,scale=TRUE)

#scale testing
feat_rest_test_s<- scale(as.matrix(feat_rest_test%>%select(-creation_time)
                                                                  , center=TRUE,scale=TRUE),
                                                                     attr(feat_rest_train_s, "scaled:center"),
                                                                        attr(feat_rest_train_s, "scaled:scale") )


##Transform both sets
feat_rest_train<-as.data.frame(feat_rest_train_s[,])
feat_rest_test<-as.data.frame(feat_rest_test_s[,])

## Check
feat_rest_train[1:5,1:5]
feat_rest_test[1:5,1:5]

### Scale alt
#feat_rest_test<- scale(as.matrix(feat_rest_test), center = mean(feat_rest_train), scale = sd(feat_rest_train) ))



# #to data frame
# feat_rest_train_s<-as.data.frame(feat_rest_train_s)
#     feat_rest_test_s<-as.data.frame(feat_rest_test_s)
# 
# 
# ##############################################3
# rep_rest<-cbind(train.mean = lapply(feat_rest_train_s[,-1], mean),
#                      train.sd = lapply(feat_rest_train_s[,-1], sd),
#                            test.mean = lapply(feat_rest_test_s[,-1], mean),
#                                 test.sd = lapply(feat_rest_test_s[,-1], sd))
# head(rep_rest)


##############################################3

# 
# ### check in detail
# library(xda)
# xdatrain<-numSummary(feat_rest_train_s)
# head(xdatrain)
# xdatest<-numSummary(feat_rest_test_s)
# head(xdatest)
# #xdatab2<-charSummary(tab3)
```

```{r warning= FALSE, message=FALSE ,fig.align = 'center' }


#scale train
feat_X3D_train_s<- scale(as.matrix(feat_X3D_train), center=TRUE,scale=TRUE)

#scale testing
feat_X3D_test_s<- scale(as.matrix(feat_X3D_test),
                         attr(feat_X3D_train_s, "scaled:center"),
                                        attr(feat_X3D_train_s, "scaled:scale") )


##Transform both sets
feat_X3D_train<-as.data.frame(feat_X3D_train_s[,])
feat_X3D_test<-as.data.frame(feat_X3D_test_s[,])

## Check
feat_X3D_train[1:5,1:5]
feat_X3D_test[1:5,1:5]
# 
# #to data frame
# feat_X3D_train_s<-as.data.frame(feat_X3D_train_s)
#     feat_X3D_test_s<-as.data.frame(feat_X3D_test_s)
# 
# 
# ##############################################3
# rep_X3D<-cbind(train.mean = lapply(feat_X3D_train_s[,-1], mean),
#                      train.sd = lapply(feat_X3D_train_s[,-1], sd),
#                            test.mean = lapply(feat_X3D_test_s[,-1], mean),
#                                 test.sd = lapply(feat_X3D_test_s[,-1], sd))
# head(rep_X3D)
# 
# 
# ##############################################3
# 
# 
# ### check in detail
# library(xda)
# xdatrain<-numSummary(feat_X3D_train_s)
# head(xdatrain)
# xdatest<-numSummary(feat_X3D_test_s)
# head(xdatest)
#xdatab2<-cha
```


```{r warning= FALSE, message=FALSE ,fig.align = 'center' }

#scale train
feat_pixel_train_s<- scale(as.matrix(feat_pixel_train), center=TRUE,scale=TRUE)

#scale testing
feat_pixel_test_s<- scale(as.matrix(feat_pixel_test),
                         attr(feat_pixel_train_s, "scaled:center"),
                                        attr(feat_pixel_train_s, "scaled:scale") )

##Transform both sets
feat_pixel_train<-as.data.frame(feat_pixel_train_s[,])
feat_pixel_test<-as.data.frame(feat_pixel_test_s[,])

## Check
feat_pixel_train[1:5,1:5]
feat_pixel_test[1:5,1:5]

# 
# 
# 
# #to data frame
# feat_pixel_train_s<-as.data.frame(feat_pixel_train_s)
#     feat_pixel_test_s<-as.data.frame(feat_pixel_test_s)
# 
# 
# ##############################################3
# rep_pixel<-cbind(train.mean = lapply(feat_pixel_train_s[,-1], mean),
#                      train.sd = lapply(feat_pixel_train_s[,-1], sd),
#                            test.mean = lapply(feat_pixel_test_s[,-1], mean),
#                                 test.sd = lapply(feat_pixel_test_s[,-1], sd))
# head(rep_pixel)
# 
# 
# ##############################################3
# 
# 
# ### check in detail
# library(xda)
# xdatrain<-numSummary(feat_pixel_train_s)
# head(xdatrain)
# xdatest<-numSummary(feat_pixel_test_s)
# head(xdatest)
# #xdatab2<-cha
```



### correlation  ~pixel features
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }
####################################################################################################################
#Elegimos las componentes a utilizar
num.cols <- names(which(sapply(feat_pixel_train, function(x) is.numeric(x) )))

set.seed(1234)
num.cols<- sample(num.cols, 100)

svd_seq<-feat_pixel_train[,num.cols ]
# Correlation scatter plots for all combinations between the first four principal components.
library(reshape2)
cormat <- round(cor(svd_seq),4)
melted_cormat <- melt(cormat)
head(melted_cormat)


p<-ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
ggplotly(p)
```

### PCA from ~pixel features
```{r warning= FALSE, message=FALSE }

# conduct PCA on training dataset
num.cols <- names(which(sapply(feat_pixel_train, function(x) is.numeric(x) )))

pca <- prcomp(feat_pixel_train[,num.cols], retx=TRUE, center=FALSE, scale=FALSE)
#Eigenvalues
eig <- (pca$sdev)^2 ; variance <-eig*100/sum(eig) ; cumvar <- cumsum(variance) ; Comp<- 1:length(cumvar)

p<-as.data.frame(cbind(Comp,cumvar)) %>%
                ggplot(aes(x =factor(Comp), y = cumvar)) + 
                    geom_bar(stat = "identity")  + geom_hline(yintercept=95, col="red") +
                            xlab("components  ~pixel features ")
ggplotly(p)
#Replace features by PCA components
feat_pixel_train_pca<-as.data.frame(pca$x[,1:100])
colnames(feat_pixel_train_pca)<-paste("pca_pixel_",1:100,sep="")

### APPLY TO TESTING DATA 
feat_pixel_test_pca<-as.data.frame(predict(pca, newdata=feat_pixel_test[,num.cols])[,1:100])
colnames(feat_pixel_test_pca)<-paste("pca_pixel_",1:100,sep="")


```


### scatter first 4 dimensions
```{r warning= FALSE, message=FALSE ,fig.width = 10, fig.height = 10 , fig.align = 'center' }

library(plotly)

pc<-as.data.frame(pca$x[,1:4])%>%
                      rename(Dim1=PC1,
                             Dim2=PC2,
                             Dim3=PC3,
                             Dim4=PC4)

p <- plot_ly(pc, x = ~Dim1, y = ~Dim2, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim2')))

p

p <- plot_ly(pc, x = ~Dim1, y = ~Dim3, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim3')))

p

p <- plot_ly(pc, x = ~Dim2, y = ~Dim4, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim4')))

p


```

### correlation  ~X3D features
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }
####################################################################################################################
#Elegimos las componentes a utilizar
num.cols <- names(which(sapply(feat_X3D_train, function(x) is.numeric(x) )))

svd_seq<-feat_X3D_train[,num.cols ]
# Correlation scatter plots for all combinations between the first four principal components.
library(reshape2)
cormat <- round(cor(svd_seq),4)
melted_cormat <- melt(cormat)
head(melted_cormat)


p<-ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
ggplotly(p)
```


### PCA from ~X3D features
```{r warning= FALSE, message=FALSE }

# conduct PCA on training dataset
num.cols <- names(which(sapply(feat_X3D_train, function(x) is.numeric(x) )))

pca <- prcomp(feat_X3D_train[,num.cols], retx=TRUE, center=FALSE, scale=FALSE)
#Eigenvalues
eig <- (pca$sdev)^2 ; variance <-eig*100/sum(eig) ; cumvar <- cumsum(variance) ; Comp<- 1:length(cumvar)

p<-as.data.frame(cbind(Comp,cumvar)) %>%
                ggplot(aes(x =factor(Comp), y = cumvar)) + 
                                            geom_bar(stat = "identity")  + geom_hline(yintercept=95, col="red") +
                            xlab("components  ~X3D features ")
ggplotly(p)
#Replace features by PCA components
feat_X3D_train_pca<-as.data.frame(pca$x[,1:10])
colnames(feat_X3D_train_pca)<-paste("pca_X3D_",1:10,sep="")

### Apply to testing
feat_X3D_test_pca<-as.data.frame(predict(pca, newdata=feat_X3D_test[,num.cols])[,1:10])
colnames(feat_X3D_test_pca)<-paste("pca_X3D_",1:10,sep="")
```

### scatter first 4 dimensions
```{r warning= FALSE, message=FALSE ,fig.width = 10, fig.height = 10 , fig.align = 'center' }

library(plotly)

pc<-as.data.frame(pca$x[,1:4])%>%
                      rename(Dim1=PC1,
                             Dim2=PC2,
                             Dim3=PC3,
                             Dim4=PC4)

p <- plot_ly(pc, x = ~Dim1, y = ~Dim2, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim2')))

p

p <- plot_ly(pc, x = ~Dim1, y = ~Dim3, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim3')))

p

p <- plot_ly(pc, x = ~Dim2, y = ~Dim4, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim4')))

p


```


### Análisis de correlación
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }
####################################################################################################################
#Elegimos las componentes a utilizar
num.cols <- names(which(sapply(feat_rest_train, function(x) is.numeric(x) )))

svd_seq<-feat_rest_train[,num.cols ]
# Correlation scatter plots for all combinations between the first four principal components.
library(reshape2)
cormat <- round(cor(svd_seq),4)
melted_cormat <- melt(cormat)
head(melted_cormat)


p<-ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
ggplotly(p)
```


### PCA from ~rest features
```{r warning= FALSE, message=FALSE }

# conduct PCA on training dataset
num.cols <- names(which(sapply(feat_rest_train, function(x) is.numeric(x) )))

pca <- prcomp(feat_rest_train[,num.cols], retx=TRUE, center=FALSE, scale=FALSE)
#Eigenvalues
eig <- (pca$sdev)^2 ; variance <-eig*100/sum(eig) ; cumvar <- cumsum(variance) ; Comp<- 1:length(cumvar)

p<-as.data.frame(cbind(Comp,cumvar)) %>%
                ggplot(aes(x =factor(Comp), y = cumvar)) + 
                                            geom_bar(stat = "identity")  + geom_hline(yintercept=95, col="red") +
                            xlab("components  ~X3D features ")
ggplotly(p)
#Replace features by PCA components
feat_rest_train_pca<-as.data.frame(pca$x[,1:12])
colnames(feat_rest_train_pca)<-paste("pca_rest_",1:12,sep="")

## Apply to testing
feat_rest_test_pca<-as.data.frame(predict(pca, newdata=feat_rest_test[,num.cols])[,1:12])
colnames(feat_rest_test_pca)<-paste("pca_rest_",1:12,sep="")
```


### scatter first 4 dimensions
```{r warning= FALSE, message=FALSE ,fig.width = 10, fig.height = 10 , fig.align = 'center' }

library(plotly)

pc<-as.data.frame(pca$x[,1:4])%>%
                      rename(Dim1=PC1,
                             Dim2=PC2,
                             Dim3=PC3,
                             Dim4=PC4)

p <- plot_ly(pc, x = ~Dim1, y = ~Dim2, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim2')))

p

p <- plot_ly(pc, x = ~Dim1, y = ~Dim3, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim3')))

p

p <- plot_ly(pc, x = ~Dim2, y = ~Dim4, color = ~as.factor(train_index$type_cat)) %>%
  layout(scene = list(xaxis = list(title = 'Dim1'),
                     yaxis = list(title = 'Dim4')))

p



```




### Análisis de correlación X3D + PCA
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }
testcor<-cbind(feat_X3D_train_pca, feat_X3D_train)

svd_seq<-testcor
# Correlation scatter plots for all combinations between the first four principal components.
library(reshape2)
cormat <- round(cor(svd_seq),4)
melted_cormat <- melt(cormat)
head(melted_cormat)


p<-ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()
ggplotly(p)


#feat_X3D_train_pca, feat_X3D_train, feat_pixel_train_pca,feat_rest_train_pca

```



#Generate outputs
```{r warning= FALSE, message=FALSE ,fig.align = 'center' }
train2<-cbind(train_index, feat_rest_train_pca, feat_X3D_train, feat_X3D_train_pca,  feat_pixel_train_pca)
test2<-cbind(test_index,feat_rest_test_pca, feat_X3D_test, feat_X3D_test_pca,  feat_pixel_test_pca)
write.csv(train2,"../../output/features/Andrei/old/ccs.new_train_v1.csv",row.names = FALSE )
write.csv(test2,"../../output/features/Andrei/old/ccs.new_test_v1.csv",row.names = FALSE )

```
